### 2010-02-05 doc/manuals/configuration/configuration_manual.tex
Added GACL, XACL and service PDPs

\subsection{Simple List}
This PDP matches X.509 subject of client certificate to list of predefined values.
Its plugin name is \texttt{simplelist.pdp} and it resides in \texttt{arcshc} loadable
module.

@@

\subsubsection{ARC}\label{sec:arc-pdp}
This plugin applies authorization policy written in ARC Policy language to attributes
of the message. Its plugin name is \texttt{arc.pdp} and it resides in \texttt{arcshc}
loadable module. For more information about ARC Policy language please "Security 
Framework of ARC NOX" \cite{arc1-sec}.

@@

\subsubsection{GACL}

\subsubsection{XACML}

@@

\subsubsection{Service Invoker}

>>>>

\subsubsection{Simple List}
This PDP matches X.509 subject of client certificate to list of predefined values.
Its plugin name is \texttt{simplelist.pdp} and it resides in \texttt{arcshc} loadable
module.

@@

\subsubsection{ARC}\label{sec:arc-pdp}
This plugin applies authorization policy written in ARC Policy language to attributes
of the message. Its plugin name is \texttt{arc.pdp} and it resides in \texttt{arcshc}
loadable module. For more information about ARC Policy language please see "Security 
Framework of ARC NOX" \cite{arc1-sec}. That docment also describes security
attributes produced by different components of ARC which can be included in policies.

@@

\subsubsection{GACL}\label{gacl-pdp}
This PDP shares configuration parameters and provides functionality similar to ARC PDP
described in the section \ref{sec:arc-pdp}. Its plugin name is \texttt{gacl.pdp} and it
resides in the same \texttt{arcshc} loadable module.

This plugin accepts policies written in GACL instead of ARC language. For more information
about GACL prease check "The Gridsite Web" \cite{gacl} and "GACL Mini-Howto" \cite{gacl-mini}.

\subsubsection{XACML}\label{xacml-pdp}
This plugin's configuration and functionality are similar to previously described ARC and
GACL PDPs.  Its plugin name is \texttt{xacml.pdp} and it resides in the same \texttt{arcshc}
loadable module.

This plugin accepts policies written in subset of XACML language \cite{xacml}. Currently 
XACML functionality is not complete yet. For more information see \cite{arc1-sec}.

@@

\subsubsection{Service Invoker}\label{service-pdp}
This plugin comunicates with possibly remote authorization service by passing it authorization
request and getting back authorization decision. Its plugin name is \texttt{pdpservice.invoker}
and it resides in \texttt{arcshc} loadable module.

The configuration element \texttt{Filter} is similar to those in other PDPs.

To specify service to be contacted \texttt{ServiceEndpoint} element is used. It contains
contact URL of service. Service is expected to accept SOAP over HTTP(S) messages conforming
to protocol defined in \texttt{TransferProtocol} configuration element. Possible options
are \texttt{arc} for ARC own protocol and \texttt{saml} for "SAML 2.0 Profile of the XACML 2.0"
kind of exchange. The format of payload - authorization request and response - is controlled
using \texttt{RequestFormat} element. Implemented are \texttt{xacml} and \texttt{arc} options
for XACML conforming or ARC specific formats respectively.

For establishing TLS communication channel to the service PDP needs to apply X.509 credentials.
For that configuration elements \texttt{CertificatePath} and \texttt{KeyPath} are used.
Alternatively if PDP uses X.509 Proxy Certificate path to file containing proxy may be
specified in \texttt{ProxyPath}.

For verifying credentials presented by service trusted CA certificates are specified through
\texttt{CACertificatePath} and \texttt{CACertificatesDir} for single file and directory 
containing multiple files respectively.
